Ice sheet mass flows

### 2024-06-05 sankey.tex
Move mass loss to top left. Align right edge.

    \ifthenelse{\Q{MG} > \Q{ML}}
    {
      \sankeynode{name=f1, quantity=\Q{RFZ}+\qq{f0},
        at={[yshift=-15mm,xshift=-3mm]f0.right}, anchor=right,
        forked={\qq{f0}/f0-in, \Q{RFZ}/RFZ-in}}
    }
    {
      \sankeynode{name=f1, quantity=\Q{RFZ}+\qq{f0}+\Q{ML},
        at={[yshift=-15mm]f0.center}, anchor=center,
        forked={\Q{ML}/ML-in, \qq{f0}/f0-in, \Q{RFZ}/RFZ-in}}
    }

@@

    \ifthenelse{\Q{MG} < \Q{ML}}
      {
        %% mass loss
        \sankeynode{name=fML, quantity=\Q{ML}, at={[xshift=\xoff,yshift=0mm]SF.left}, anchor=right}%, angle=-145}
        \sankeystart[red]{fML}
        \sankeyadvance[red-to-ice]{fML}{5mm}
        \sankeyoutin{fML}{ML-in}
      }
      {
        %% mass gain
        \sankeyadvance[ice-to-black]{fMGa}{3mm}
        \sankeyend[black]{fMGa}
      }

>>>>

    \ifthenelse{\Q{MG} > \Q{ML}}
    { % mass gain
      \sankeynode{name=f1, quantity=\Q{RFZ}+\qq{f0},
        at={[yshift=-15mm]f0.left}, anchor=left,
        forked={\qq{f0}/f0-in, \Q{RFZ}/RFZ-in}}
    }
    { % mass loss
      \sankeynode{name=f1, quantity=\Q{RFZ}+\qq{f0}+\Q{ML},
        at={[yshift=-15mm]f0.left}, anchor=left,
        forked={\qq{f0}/f0-in, \Q{ML}/ML-in, \Q{RFZ}/RFZ-in}}
    }

@@

    \ifthenelse{\Q{MG} < \Q{ML}}
      {
        %% mass loss
        \sankeynode{name=fML, quantity=\Q{ML},
          at={[xshift=-\xoff]RF.right}, anchor=left} %, angle=-45}
        \sankeystart[red]{fML}
        \sankeyadvance[red-to-ice]{fML}{5mm}
        \sankeyoutin{fML}{ML-in}
      }
      {
        %% mass gain
        \sankeyadvance[ice-to-black]{fMGa}{3mm}
        \sankeyend[black]{fMGa}
      }
